\item    {\bf OnlineHistDB }(std::string passwd,\\\mbox{}~~~~~~~~~ 
		std::string user=OnlineHistDBEnv\_constants::ACCOUNT,\\\mbox{}~~~~~~~~~ 
		std::string db=OnlineHistDBEnv\_constants::DB);

 constructor


\item    bool {\bf commit}();


 commits all changes to the DB. Returns true if there are no errors.


\item    void {\bf setHistogramBufferDepth}(int N);


 when creating histograms with the {\it declareHistByServiceName}
 method, the histogram list is actually send to the DB server every N
 histograms (or at commit) in order to optimize performance. The
 default buffer depth (recommended value) is 1000. 


\item    bool {\bf declareTask}(std::string Name,\\\mbox{}~~~~~~~~~ 
		   std::string SubDet1="NULL",\\\mbox{}~~~~~~~~~ 
		   std::string SubDet2="NULL",\\\mbox{}~~~~~~~~~ 
		   std::string SubDet3="NULL",\\\mbox{}~~~~~~~~~
		   bool RunsOnPhysics=false,\\\mbox{}~~~~~~~~~ 
		   bool RunsOnCalib=false,\\\mbox{}~~~~~~~~~ 
		   bool RunsOnEmpty=false,\\\mbox{}~~~~~~~~~
		   float SavingFrequency=0);

 declares a new task to the DB, or updates its configuration 


\item    OnlineHistTask* {\bf getTask}(std::string Name);


 get an OnlineHistTask object, holding informations of an existing task, that can be used to view/edit a task record


\item    OnlineHistogram* {\bf getHistogram}(std::string Identifier,\\\mbox{}~~~~~~~~~
				std::string FullPathPageName="\_NONE\_",\\\mbox{}~~~~~~~~~
				int Instance = 1);

 gets a pointer to an OnlineHistogram object that can be used to view/edit an histogram record. If FullPathPageName
 is specified, the default display options for the histogram are those associated to the page (if available).
 Uses cached histogram objects if available


\item    OnlineHistogram* {\bf getNewHistogram}(std::string Identifier,\\\mbox{}~~~~~~~~~
				   std::string FullPathPageName="\_NONE\_",\\\mbox{}~~~~~~~~~
				   int Instance = 1);

 same as getHistogram, but a new object is always created (no caching)


\item    virtual bool {\bf removeHistogram}(OnlineHistogram* h,\\\mbox{}~~~~~~~~~
			       bool RemoveWholeSet = false);

 removes an histogram, and optionally its full set. 
 ({\bf TEMPORARY METHOD TO BE REMOVED AT PRODUCTION STAGE})


\item    OnlineHistPage* {\bf getPage}(std::string Name);


 get an OnlineHistPage object, to create a new page or view/edit an existing one


\item    bool {\bf removePage}(OnlineHistPage* Page);


 removes completely the page, and all associated options (HANDLE WITH CARE!)


\item    bool {\bf declareSubSystem}(std::string SubSys);


 declares a  subsystem, returning true on success


\item    void {\bf declareHistByServiceName}(const std::string \&ServiceName);


 declares an Histogram by its DIM service name. In the LHCb
 DAQ, this is intended to be used only by the Experiment Control
 System to dynamically update the DB with the published histograms.
 Tasks not known to the DB are automatically created.
 If histogram already exists, just updates the current DIM service name 


\item    void {\bf declareHistogram}(std::string TaskName,\\\mbox{}~~~~~~~~~
			std::string AlgorithmName,\\\mbox{}~~~~~~~~~
			std::string HistogramName,\\\mbox{}~~~~~~~~~
			HistType Type);

 declares an Histogram to the DB by its attributes.  The enum HistType is defined in class OnlineHistDBEnv


\item    bool {\bf sendHistBuffer}();


 forces sending histogram declaration buffer to the DB. Returns true if there are no errors.


\item    OnlineHistogram* {\bf declareAnalysisHistogram}(std::string Algorithm,\\\mbox{}~~~~~~~~~
					    std::string Name,\\\mbox{}~~~~~~~~~
					    std::vector$<$OnlineHistogram*$>$ \&Sources,\\\mbox{}~~~~~~~~~
					    std::vector$<$float$>$* Parameters = NULL);

 declares an histogram to be produced at analysis
 level using algorithm Algorithm. Name is the histogram name. Sources
 must contain the pointers to the input histograms. Parameters is a
 pointer to a parameter vector, optionally needed by the algorithm. If
 the algorithm requires an histogram set as input, use any histogram of the
 set. Returns the pointer to the new histogram object.


\item    bool {\bf declareCheckAlgorithm}(std::string Name,\\\mbox{}~~~~~~~~~ 
			     int Npars,\\\mbox{}~~~~~~~~~ 
			     std::vector$<$std::string$>$ *pars=NULL,\\\mbox{}~~~~~~~~~ 
			     std::string doc="NONE");

 declares to the DB an Analysis algorithm implemented in the Analysis
 library. Npars is the number of algorithm's parameters, pars should
 point to an array containing the parameter names, doc is a short
 description of the algorithm.


\item    bool {\bf declareCreatorAlgorithm}(std::string Name,\\\mbox{}~~~~~~~~~ 
			       int Ninput=0,\\\mbox{}~~~~~~~~~ 
			       HistType OutputType = H1D,\\\mbox{}~~~~~~~~~
			       int Npars=0,\\\mbox{}~~~~~~~~~ 
			       std::vector$<$std::string$>$ *pars=NULL,\\\mbox{}~~~~~~~~~
			       std::string doc="NONE");

 declares to the DB an available algorithm to produce histograms at
 analysis time. Ninput is the number of input histograms, Npars the
 number of optional parameters (pars containing their names), doc is a short
 description of the algorithm.


\item    bool {\bf removePageFolder}(std::string Folder);


 removes Page Folder only if it doesn't have pages (useful for cleanup)


\item    int {\bf getAlgListID}() const ;

 gets the algorithm list version


\item    bool {\bf setAlgListID}(int algListID);


 sets the algorithm list version (works only for DB admin account)


\item    int {\bf getAlgorithmNpar}(std::string AlgName,\\\mbox{}~~~~~~~~~
		       int* Ninput = NULL) const;

 gets the number of parameters, and optionally the number of input histograms, needed by algorithm AlgName.


\item    std::string {\bf getAlgParName}(std::string AlgName,\\\mbox{}~~~~~~~~~
		       int Ipar) const;

 gets the name of parameter Ipar (starting from 1) of algorithm AlgName


\item    int {\bf getAllHistograms}(std::vector$<$OnlineHistogram*$>$* list = NULL,\\\mbox{}~~~~~~~~~
		       std::vector$<$string$>$* ids = NULL,\\\mbox{}~~~~~~~~~
		       std::vector$<$string$>$* types = NULL);

 gets the full list of histograms. Returns the number of histograms found. Vectors with pointers
 to OnlineHistogram objects, histogram identifiers, histogram types can optionally created  by the user
 and filled if not null


\item    int {\bf getHistogramsWithAnalysis}(std::vector$<$OnlineHistogram*$>$* list = NULL,\\\mbox{}~~~~~~~~~
				std::vector$<$string$>$* ids = NULL,\\\mbox{}~~~~~~~~~
				std::vector$<$string$>$* types = NULL);

 gets the list of histograms on which some check analysis has to be performed 


\item    int {\bf getAnalysisHistograms}(std::vector$<$OnlineHistogram*$>$* list = NULL,\\\mbox{}~~~~~~~~~
			    std::vector$<$string$>$* ids = NULL,\\\mbox{}~~~~~~~~~
			    std::vector$<$string$>$* types = NULL);

 gets the list of histograms that have to be produced by analysis task


\item    int {\bf getHistogramsBySubsystem}(std::string SubSys,\\\mbox{}~~~~~~~~~
			       std::vector$<$OnlineHistogram*$>$* list = NULL,\\\mbox{}~~~~~~~~~
			       std::vector$<$string$>$* ids = NULL,\\\mbox{}~~~~~~~~~
			       std::vector$<$string$>$* types = NULL);

 gets the list of histograms related to subsystem SubSys


\item    int {\bf getHistogramsByTask}(std::string Task,\\\mbox{}~~~~~~~~~
			  std::vector$<$OnlineHistogram*$>$* list = NULL,\\\mbox{}~~~~~~~~~
			  std::vector$<$string$>$* ids = NULL,\\\mbox{}~~~~~~~~~
			  std::vector$<$string$>$* types = NULL);

 gets the list of histograms related to task Task


\item    int {\bf getHistogramsByPage}(std::string Page,\\\mbox{}~~~~~~~~~
			  std::vector$<$OnlineHistogram*$>$* list = NULL,\\\mbox{}~~~~~~~~~
			  std::vector$<$string$>$* ids = NULL,\\\mbox{}~~~~~~~~~
			  std::vector$<$string$>$* types = NULL);

 gets the list of histograms displayed on page Page


\item    int {\bf getHistogramsBySet}(std::string SetName,\\\mbox{}~~~~~~~~~
			 std::vector$<$OnlineHistogram*$>$* list = NULL,\\\mbox{}~~~~~~~~~
			 std::vector$<$string$>$* ids = NULL,\\\mbox{}~~~~~~~~~
			 std::vector$<$string$>$* types = NULL);

 gets the list of histograms in a Set


\item    int {\bf getPageFolderNames}(std::vector$<$string$>$\& list,\\\mbox{}~~~~~~~~~ std::string Parent="\_ALL\_");


 gets the list of page folders, Parent can be "/", a page folder name or "\_ALL\_" for all folders  


\item    int {\bf getPageNamesByFolder}(std::string Folder,\\\mbox{}~~~~~~~~~
			   std::vector$<$string$>$\& list);

 gets the list of pages in a folder


\item    int {\bf getSubsystems}(std::vector$<$string$>$\& list);


 gets the list of known subsystems


\item    int {\bf getTasks}(std::vector$<$string$>$\& list);


 gets the list of tasks


\item    int {\bf getAlgorithms}(std::vector$<$string$>$\& list,\\\mbox{}~~~~~~~~~std::string type="\_ALL\_");


 gets the list of algorithms, type can be "\_ALL\_", "CHECK", "HCREATOR"


